Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2022-04-20 doc/manuscript/ESSDmanuscript.Rmd
misc

n_records_checked = NA # this will be hard to get at, but we can at least estimate a minimum (= previously existing records in records sent to EFDB)
n_records_added = max(ForC_measurements$measurement.ID) -48956 # Madison's entries start with measurement.ID = 48956

@@

As of `r format(Sys.time(), '%B %d, %Y')`<!--inserts date upon knit-->, we had reviewed and sent `r n_records_sent_to_EFDB` records to EFDB, `r n_records_posted_EFDB` of which have been reviewed, accepted, and posted (Figs. `r fig_map`-`r fig_histograms`, Table `r table_variables`).
*[DETAILS]*

>>>>

n_records_reviewed_or_added= NA
n_records_added = max(ForC_measurements$measurement.ID) -48956 # Madison's entries start with measurement.ID = 48956
n_records_checked = n_records_reviewed_or_added - n_records_added # this will be hard to get at, but we can at least estimate a minimum (= previously existing records in records sent to EFDB)

@@

As of `r format(Sys.time(), '%B %d, %Y')`<!--inserts date upon knit-->, we had reviewed or added `r n_records_reviewed_or_added` EFDB-relevant records, `r n_records_sent_to_EFDB` records of which were sent to EFDB, and `r n_records_posted_EFDB` of which have been reviewed, accepted, and posted (Figs. `r fig_map`-`r fig_histograms`, Table `r table_variables`).
*[DETAILS]*

### 2022-04-20 doc/manuscript/ESSDmanuscript.tex
knit in new table
#36
misc

\begin{longtabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\caption{\label{tab:table_variables}\textbf{Numbers of records of ForC variables relevant to, and sent to, EFDB.} Relationships of variables to IPCC-defined forest C pools (Table 1) and to each other are illustrated in Figure 1. }\\
\hline
\textbf{variable} & \textbf{n in ForC} & \textbf{n independent records in ForC} & \textbf{n reviewed} & \textbf{n sent to EFDB}\\
\hline
\textbf{Biomass} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
biomass &  &  &  & \\
\hline
delta.biomass &  &  &  & \\
\hline
NPP\_woody &  &  &  & \\
\hline
woody.mortality &  &  &  & \\
\hline
\textbf{Aboveground biomass} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
biomass\_ag &  &  &  & \\
\hline
biomass\_ag\_woody &  &  &  & \\
\hline
biomass\_ag\_foliage &  &  &  & \\
\hline
delta.agb &  &  &  & \\
\hline
ANPP\_woody &  &  &  & \\
\hline
ANPP\_foliage &  &  &  & \\
\hline
woody.mortality\_ag &  &  &  & \\
\hline
\textbf{Belowground biomass} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
biomass\_root &  &  &  & \\
\hline
biomass\_root\_fine &  &  &  & \\
\hline
biomass\_root\_coarse &  &  &  & \\
\hline
delta.biomass\_root &  &  &  & \\
\hline
delta.biomass\_root\_coarse &  &  &  & \\
\hline
delta.biomass\_root\_fine &  &  &  & \\
\hline
woody.mortality\_root &  &  &  & \\
\hline
BNPP\_root\_fine &  &  &  & \\
\hline
BNPP\_root.turnover\_fine &  &  &  & \\
\hline
BNPP\_root\_coarse &  &  &  & \\
\hline
\textbf{Dead wood} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
deadwood &  &  &  & \\
\hline
deadwood\_standing &  &  &  & \\
\hline
deadwood\_down &  &  &  & \\
\hline
delta.deadwood &  &  &  & \\
\hline
delta.deadwood\_standing &  &  &  & \\
\hline
delta.deadwood\_down &  &  &  & \\
\hline
R\_het\_deadwood & 0 &  &  & \\
\hline
\textbf{Litter} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
O.horizon &  &  &  & \\
\hline
delta.O.horizon &  &  &  & \\
\hline
litter &  &  &  & \\
\hline
delta.litter &  &  &  & \\
\hline
NPP\_litterfall &  &  &  & \\
\hline
R\_het\_litter &  &  &  & \\
\hline
\textbf{Soil organic matter} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
SOM / SOC &  &  &  & \\
\hline
delta.SOM / delta.SOC &  &  &  & \\
\hline
R\_het\_soil &  &  &  & \\
\hline
\textbf{TOTAL} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
\end{longtabu}

@@

As of April 20, 2022, we had reviewed and sent NA records to EFDB, 73 of
which have been reviewed, accepted, and posted (Figs. 2-3, Table 2).
\emph{{[}DETAILS{]}}

>>>>

\begin{longtabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\caption{\label{tab:table_variables}\textbf{Numbers of records of ForC variables relevant to, and sent to, EFDB.} Relationships of variables to IPCC-defined forest C pools (Table 1) and to each other are illustrated in Figure 1. }\\
\hline
\textbf{variable} & \textbf{n in ForC} & \textbf{n independent records in ForC} & \textbf{n reviewed} & \textbf{n sent to EFDB}\\
\hline
\textbf{Biomass} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
biomass & 1095 & 847 & 93 & 48\\
\hline
delta.biomass & 0 & 0 & 0 & 0\\
\hline
NPP\_woody & 136 & 93 & 0 & 0\\
\hline
woody.mortality & 0 & 0 & 0 & 0\\
\hline
\textbf{Aboveground biomass} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
biomass\_ag & 9038 & 7721 & 1230 & 693\\
\hline
biomass\_ag\_woody & 460 & 366 & 10 & 10\\
\hline
biomass\_ag\_foliage & 601 & 502 & 49 & 27\\
\hline
delta.agb & 166 & 128 & 123 & 123\\
\hline
ANPP\_woody & 299 & 242 & 0 & 0\\
\hline
ANPP\_foliage & 0 & 0 & 0 & 0\\
\hline
woody.mortality\_ag & 113 & 59 & 17 & 17\\
\hline
\textbf{Belowground biomass} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
biomass\_root & 4629 & 4180 & 123 & 55\\
\hline
biomass\_root\_fine & 931 & 594 & 18 & 18\\
\hline
biomass\_root\_coarse & 599 & 410 & 12 & 7\\
\hline
delta.biomass\_root & 0 & 0 & 0 & 0\\
\hline
delta.biomass\_root\_coarse & 0 & 0 & 0 & 0\\
\hline
delta.biomass\_root\_fine & 0 & 0 & 0 & 0\\
\hline
woody.mortality\_root & 0 & 0 & 0 & 0\\
\hline
BNPP\_root\_fine & 489 & 332 & 0 & 0\\
\hline
BNPP\_root.turnover\_fine & 91 & 56 & 0 & 0\\
\hline
BNPP\_root\_coarse & 329 & 250 & 0 & 0\\
\hline
\textbf{Dead wood} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
deadwood & 438 & 301 & 94 & 61\\
\hline
deadwood\_standing & 152 & 120 & 17 & 17\\
\hline
deadwood\_down & 424 & 368 & 51 & 27\\
\hline
delta.deadwood & 0 & 0 & 0 & 0\\
\hline
delta.deadwood\_standing & 0 & 0 & 0 & 0\\
\hline
delta.deadwood\_down & 0 & 0 & 0 & 0\\
\hline
R\_het\_deadwood & 0 & 0 & 0 & 0\\
\hline
\textbf{Litter} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
O.horizon & 38 & 38 & 38 & 38\\
\hline
delta.O.horizon & 4 & 4 & 4 & 4\\
\hline
litter & 30 & 30 & 23 & 23\\
\hline
delta.litter & 0 & 0 & 0 & 0\\
\hline
NPP\_litter & 0 & 0 & 0 & 0\\
\hline
R\_het\_litter & 167 & 143 & 0 & 0\\
\hline
\textbf{Soil organic matter} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
SOM / SOC & 693 & 396 & 79 & 46\\
\hline
delta.SOM / delta.SOC & 0 & 0 & 0 & 0\\
\hline
R\_het\_soil & 0 & 0 & 0 & 0\\
\hline
\textbf{TOTAL} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
\end{longtabu}

@@

As of April 20, 2022, we had reviewed or added NA EFDB-relevant records,
NA records of which were sent to EFDB, and 73 of which have been
reviewed, accepted, and posted (Figs. 2-3, Table 2).
\emph{{[}DETAILS{]}}
